\cvsection{Peer Reviewed Publications}

\begin{cvparagraph}
    \textbf{Blumberg, W.G.}, and A. Fadl, 2021: {Assessing the Impact of Meteorological Assumptions on Distant Focusing Overpressure Risk at Simulated Coastal U.S. Launch Ranges}, \emph{J. Appl. Met. Climo.}, in progress. % Type

    \textbf{Blumberg, W.G.}, S. C. Tsay, and U. Jeong, 2021:  {Mountain-Valley Processes Facilitating Aerosol Upwelling During Biomass Burning Season in Northern Thailand}, \emph{J. Appl. Met. Climo.}, in progress. % Type
    
    \textbf{Blumberg, W.G.}, D. D. Turner, S. Cavallo, J. Basara, and A. Shapiro, 2021:  {Environmental Changes Supportive of Severe, Moist Convection in Northern Oklahoma during the Evening Transition}, \emph{J. Appl. Met. Climo.}, in progress. % Type

    Bolton, M. J., \textbf{W. G. Blumberg}, L. K. Ault, H. M. Mogil, and S. H. Hanes. 2020. "Initial Evidence for Increased Weather Salience in Autism Spectrum Conditions." Weather, Climate, and Society, \textbf{12} : 293-307. doi:10.1175/wcas-d-18-0100.1.

    \textbf{Blumberg, W.G.}, D. D. Turner, S. Cavallo, J. Basara, A. Shapiro, and J. Gao, 2019:  \href{https://journals.ametsoc.org/doi/abs/10.1175/JAMC-D-19-0062.1?mobileUi=0}{An Analysis of the Processes Affecting Rapid Near-Surface Water Vapor Increases during the Afternoon to Evening Transition in Oklahoma}, \emph{J. Appl. Met. Climo.}, \textbf{58}, 2217-2234, doi:10.1175/JAMC-D-19-0062.1 % Type

    Turner, D. D. and \textbf{W.G. Blumberg}, 2018: \href{https://ieeexplore.ieee.org/abstract/document/8576572}{Improvements to the AERIoe Thermodynamic Profile Retrieval Algorithm}, \emph{IEEE Sel. Top. Appl. Earth Obs. Remote Sens.}, doi:10.1109/JSTARS.2018.2874968.
    
    \textbf{Blumberg, W.G.}, T. J. Wagner, D. D. Turner, and J. Correia Jr., 2017: \href{http://journals.ametsoc.org/doi/abs/10.1175/JAMC-D-17-0036.1}{Quantifying the accuracy and uncertainty of diurnal thermodynamic profiles and convection indices from the Atmospheric Emitted Radiance Interferometer}, \emph{J. Appl. Met. Climo.}, \textbf{56}, 2747-2766, doi:10.1175/JAMC-D-17-0036.1
    
    \textbf{Blumberg, W.G.}, K. T. Halbert, T. A. Supinie, P. T. Marsh, R. L. Thompson, and J. A. Hart, 2017: \href{http://journals.ametsoc.org/doi/abs/10.1175/BAMS-D-15-00309.1}{SHARPpy: An open source sounding analysis toolkit for the atmospheric sciences}, \emph{Bull. Amer. Met. Soc.}, \textbf{98}, 1625-1636, doi:10.1175/BAMS-D-15-00309.1
    
    \textbf{Blumberg, W.G.}, D.D. Turner, U. Loehnert, and S. Castleberry, 2015: \href{http://journals.ametsoc.org/doi/abs/10.1175/JAMC-D-15-0005.1}{Ground-based temperature and humidity profiling using spectral infrared and microwave observations.  Part II: Retrieval performance in all-sky conditions}, \emph{J. Appl. Met. Climo.}, \textbf{54}, 2305-2319, doi:10.1175/JAMC-D-15-0005.1
    
    Bonin, T. A., \textbf{W.G. Blumberg}, P. M. Klein, and P. B. Chilson, 2015: \href{http://link.springer.com/article/10.1007/s10546-015-0072-2}{Thermodynamic and turbulence characteristics of the Southern Great Plains nocturnal boundary layer under differing turbulent regimes}. \emph{Boundary-Layer Meteorology}, \textbf{157}, 401-420, doi:10.1007/s10546-015-0072-2
    
    Klein P., T.A. Bonin, J.F. Newman,  D.D. Turner, P.B. Chilson, C.E. Wainwright, \textbf{W.G Blumberg}, S. Mishra, M. Carney,  E.P. Jacobsen, and R.K. Newsom, 2014: \href{http://journals.ametsoc.org/doi/abs/10.1175/BAMS-D-13-00267.1}{The 2012 lower atmospheric boundary layer experiment}. \emph{Bull. Amer. Met. Soc.}, \textbf{96}, 1743-1764, doi:10.1175/BAMS-D-132-00267.1
\end{cvparagraph}
