\cvsection{Teaching Experience}

\begin{cventries}
  \cventry
    {Instructor - Atmospheric Dynamics 2 (METR 3123)} % Job title
    {University of Oklahoma School of Meteorology} % Organization
    {Norman, OK} % Location
    {Summer 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led students through discussions and lessons in an 8-week intensive course on atmospheric dynamics concepts such as balanced flow, circulation, vorticity, Rossby wave behavior, potential vorticity, boundary layer phenomena, and differences between barotropic and baroclinic atmospheres to prepare students for senior level classes.}
      \end{cvitems}
    }

  \cventry
    {Teaching Assistant - Introduction to Meteorology 1 Lab (METR 2011)} % Job title
    {} % Organization
    {} % Location
    {Spring 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and provided assignments to improve critical thinking skills, reinforce meteorological concepts, and expose students to various tools (e.g., hand analysis, satellites, numerical weather prediction, programming, sounding analysis) used in the field of meteorology.}
      \end{cvitems}
    }
    
  \cventry
    {Teaching Assistant - Severe and Unusual Weather (METR 2603)} % Job title
    {} % Organization
    {} % Location
    {Spring 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Graded and covered classes for the primary instructor.  Course materials exposed majors and non-majors to meteorological concepts relevant to severe weather.}
      \end{cvitems}
    }
    
  \cventry
    {Teaching Assistant - Measurements Lab (METR 3613)} % Job title
    {} % Organization
    {} % Location
    {Fall 2011, 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead undergraduate junior meteorology students through lab exercises and performed assessments of their full lab reports.  }
      \end{cvitems}
    }
    
  \cventry
    {Teaching Assistant - Introduction to Weather and Climate for Non-Majors (METR 1013)} % Job title
    {} % Organization
    {} % Location
    {Spring 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and presented lessons regarding the weekly lab activity and graded lab reports.}
      \end{cvitems}
    }
    
  \cventry
    {Lead CAREERS Weather Camp Instructor} % Job title
    {Independently Contracted and Volunteer Experiences} % Organization
    {Online and in-person} % Location
    {Summer 2010, 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contracted through NCAS (NOAA Center for Atmospheric Sciences) to observe the high school level weather camp instruction and write camp evaluation reports to be used for reporting to the National Science Foundation CAREERS grant (Award \#0914676). Reports included qualitative observations of camp activities, and recommendations for how to evolve and improve future camps.}
      \end{cvitems}
    }    
  \cventry
    {Guest Instructor - WDTD/CAPS Training Programs} % Job title
    {} % Organization
    {} % Location
    {October 2016, Fall 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Trained international meteorologists from Japan and the Chinese Meteorological Agency on the severe weather forecasting process.}
        \item {Instructed visiting forecasters in ingredients-based forecasting and hand analysis using real-time data.}
        \item {Designed learning modules on the use of numerical weather prediction convection allowing models to prediction thunderstorm hazards.}
      \end{cvitems}
    }    
    
  \cventry
    {Distance Meteorology Education and Mentorship for High School Students} % Job title
    {} % Organization
    {} % Location
    {Summer 2011 - Summer 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed materials for and provided regular online forecasting and undergraduate-level meteorology education to a variety of high school students across the US.  Students demonstrated their acquired meteorological knowledge by both producing forecasts and performing research$^{2}$ that was presented at AMS conferences.  Mentorship and education were typically conducted using online methods (e.g., Skype and email).}
      \end{cvitems}
    }    
    
  \cventry
    {Coding Instructor} % Job title
    {} % Organization
    {} % Location
    {Summer 2017, 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Instructed and developed a workshop for undergraduate interns on Python coding practices and data analysis for the National Weather Center Research Experiences for Undergraduates (REU) Program.}
      \end{cvitems}
    }    
\end{cventries}
